Authors' Instructions \subtitle{Preparation of Camera-Ready Contributions to SCITEPRESS Proceedings}

### 2015-10-05 paper.tex
Cambiado el nombre de la bibliografia en paper.tex
Cambios en bibliografia para acentos y letra ñ

The {rCUDA} 5.0 client exposes the same interface as the regular NVIDIA
CUDA 6.5 release~\cite{cuda65}, including the runtime and driver
APIs as well as other commonly used libraries such as cuBLAS, cuFFT, cuSparse or cuRand.
Therefore, applications are not aware of the fact that they are being executed
on top of a virtualization layer.
With the aim to be updated with new GPU programming models, {rCUDA} also supports
directive-based models such as OmpSS~\cite{repara15} and OpenACC~\{cluster15}.

@@

\bibliographystyle{apalike}
{\small
\bibliography{example}}

>>>>

The {rCUDA} 5.0 client exposes the same interface as the regular NVIDIA
CUDA 6.5 release~\cite{cuda65}, including the runtime and driver
APIs as well as other commonly used libraries such as cuBLAS, cuFFT, cuSparse or cuRand.
Therefore, applications are not aware of the fact that they are being executed
on top of a virtualization layer.
With the aim to be updated with new GPU programming models, {rCUDA} also supports
directive-based models such as OmpSS~\cite{repara15} and OpenACC~\cite{cluster15}.

@@

\bibliographystyle{apalike}
{\small
\bibliography{paper}}
